Figure 6 - networks

### 2024-07-26 ms_figure_6_networks.Rmd
Save network data jsons with auto_unbox=TRUE

>>>>

We export the generated networks for use by TFexplorer.

```{r}
## 150 mM NaCl
n150 <- as_tbl_graph(gr150) |>
    activate(nodes) |>
    data.frame() |>
    mutate(idx = seq_along(name))
e150 <- as_tbl_graph(gr150) |>
    activate(edges) |>
    data.frame() |>
    left_join(n150 |> select(name, idx) |> rename(from = idx, from_name = name), 
              by = "from") |>
    left_join(n150 |> select(name, idx) |> rename(to = idx, to_name = name),
              by = "to")
exp150 <- list(
    nodes = lapply(seq_len(nrow(n150)), function(i) {
        list(id = n150$name[i], 
             label = n150$name[i], 
             value = 1)
    }),
    edges = lapply(seq_len(nrow(e150)), function(i) {
        list(source = e150$from_name[i],
             target = e150$to_name[i],
             value = e150$value[i])
    })
)
exp150 <- toJSON(exp150,
                 pretty = TRUE, 
                 auto_unbox = TRUE)
write(exp150, file = "data/networkData_150mMSalt.json")

## 500 mM NaCl
n500 <- as_tbl_graph(gr500) |>
    activate(nodes) |>
    data.frame() |>
    mutate(idx = seq_along(name))
e500 <- as_tbl_graph(gr500) |>
    activate(edges) |>
    data.frame() |>
    left_join(n500 |> select(name, idx) |> rename(from = idx, from_name = name), 
              by = "from") |>
    left_join(n500 |> select(name, idx) |> rename(to = idx, to_name = name),
              by = "to")
exp500 <- list(
    nodes = lapply(seq_len(nrow(n500)), function(i) {
        list(id = n500$name[i], 
             label = n500$name[i], 
             value = 1)
    }),
    edges = lapply(seq_len(nrow(e500)), function(i) {
        list(source = e500$from_name[i],
             target = e500$to_name[i],
             value = e500$value[i])
    })
)
exp500 <- toJSON(exp500,
                 pretty = TRUE, 
                 auto_unbox = TRUE)
write(exp500, file = "data/networkData_500mMSalt.json")
```
